---
output: word_document
---
Read the data from the file

```{r}
activity <- read.csv("...Desktop/activity.csv")
summary(activity)
head(activity)
library(lattice)
activity$date <- as.Date(activity$date, "%Y-%m-%d")
```

To draw the histogram of total no. of steps taken
```{r}
totalSteps <- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
summary(totalSteps)
hist(totalSteps$steps, 
     main = "Total steps by day", 
     xlab = "day", 
     ylab = "Interval",
     col = "green")
```

The mean of the total steps taken
```{r}
mean(totalSteps$steps)
```


The median of the total steps taken
```{r}
median(totalSteps$steps)
```

 
Time series plot of the steps taken with 5 min. interval with average steps taken 

```{r}
time_series <- tapply(activity$steps, activity$interval, mean, na.rm = TRUE)

plot(row.names(time_series), time_series, type = "l", 
     main = "Average number of steps taken", 
     xlab = "5-min interval", 
     ylab = "Average of all Days", 
     col = "green")
```
 
Maximum no. of steps taken during 
```{r}
max_interval <- which.max(time_series)
names(max_interval)
```

To impute missing values, first find out how many missing values are there 
```{r}
activityNA <- sum(is.na(activity))
activityNA
```

Replace the missing value by mean in 5 min interval
```{r}
StepsAverage <- aggregate(steps ~ interval, data = activity, FUN = mean)
fill_na <- numeric()
for (i in 1:nrow(activity)) {
    obs <- activity[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(StepsAverage, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    fill_na <- c(fill_na, steps)
}
```

New data set with all the filled in missing data
```{r}
activity2 <- activity
activity2$steps <- fill_na
head(activity2)
totalSteps2 <- aggregate(steps ~ date, data = activity2, sum, na.rm = TRUE)
head(totalSteps2)
```

Histogram of total no. of steps taken each day
```{r}
hist(totalSteps2$steps, main = "Total steps by day", 
     xlab = "day", 
     col = "green")
```


Calculate mean of total steps taken per day
```{r}
mean(totalSteps2$steps)
```

Calculte median of total steps taken per day
```{r}
median(totalSteps2$steps)
```

Differences in activity patterns between weekdays and weekends
 
